Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-12-09 src/tex/ms.tex
Starting funding acknowledgements.

\newcommand{\Illinois}{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green St., IL 61801, USA}
\newcommand{\NCSA}{National Center for Supercomputing Applications, Urbana, IL, 61801, USA}
\newcommand{\CAPS}{Center for AstroPhysical Surveys, Urbana, IL, 61801, USA}
\newcommand{\NSF}{National Science Foundation Graduate Research Fellow}

@@

\author[0000-0002-2495-3514]{John~Franklin~Crenshaw}
\affiliation{DIRAC Institute and the Department of Physics, University of Washington, Seattle, WA 98195, USA}

\author[0000-0002-6825-5283]{J.~Bryce~Kalmbach}
\affiliation{DIRAC Institute and the Department of Astronomy, University of Washington, Seattle, WA 98195, USA}

\author[0000-0003-4906-8447]{Alexander~Gagliano}
\affiliation{\Illinois}
\affiliation{\NCSA}
\affiliation{\CAPS}
\affiliation{\NSF}

@@

\begin{acknowledgements}
    Author contributions are listed below: \\
    J.~F.~Crenshaw: created PZFlow, designed experiments, wrote paper. \\
    J.~B.~Kalmbach: wrote early normalizing flow code that evolved into PZFlow; photo-z estimation. \\
    A.~Gagliano: validated code, developed use cases and associated tutorials; revised manuscript text. \\
    Z.~Yan: contributed to PZFlow and PhotErr. \\
    A.~J.~Connolly: discussion during development. \\
    F.~Lanusse: wrote early normalizing flow code that evolved into PZFlow. \\
    A.~I.~Malz: consulted on design and testing of PZFlow. \\
    S.~J.~Schimdt: consulted on design and testing of PZFlow and PhotErr. \\
\end{acknowledgements}

>>>>

\newcommand{\dirac}{DIRAC Institute and the Department of Astronomy, University of Washington, Seattle, WA 98195, USA}

@@

\author[0000-0002-2495-3514]{John~Franklin~Crenshaw}
\affiliation{\dirac}
\affiliation{Department of Physics, University of Washington, Seattle, WA 98195, USA}

\author[0000-0002-6825-5283]{J.~Bryce~Kalmbach}
\affiliation{\dirac}

\author[0000-0003-4906-8447]{Alexander~Gagliano}
\affiliation{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green St., IL 61801, USA}
\affiliation{National Center for Supercomputing Applications, Urbana, IL, 61801, USA}
\affiliation{Center for AstroPhysical Surveys, Urbana, IL, 61801, USA}
\affiliation{National Science Foundation Graduate Research Fellow}

@@

\begin{acknowledgements}
    J.~F.~Crenshaw, B.~J.~Kalmbach, and A.~J.~Connolly acknowledge support from the DiRAC Institute in the Department of Astronomy at the University of Washington.
    The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
    Z.~Yan acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the German Federal Ministry of Education and Research.

    Author contributions are listed below: \\
    J.~F.~Crenshaw: created PZFlow, designed experiments, wrote paper. \\
    J.~B.~Kalmbach: wrote early normalizing flow code that evolved into PZFlow; photo-z estimation. \\
    A.~Gagliano: validated code, developed use cases and associated tutorials; revised manuscript text. \\
    Z.~Yan: contributed to PZFlow and PhotErr. \\
    A.~J.~Connolly: discussion during development. \\
    F.~Lanusse: wrote early normalizing flow code that evolved into PZFlow. \\
    A.~I.~Malz: consulted on design and testing of PZFlow. \\
    S.~J.~Schimdt: consulted on design and testing of PZFlow and PhotErr. \\
\end{acknowledgements}
